% Author: Valentino Lanzarini
% Date: March-April 2026
% Project: Lanzarini Model (Geodetic-Entropic Optimization)
% Note: This document records the empirical testing of statistical 
% curvature proxies (V1-V17) which led to the development of the LP-2 Framework.


\documentclass{article}
\usepackage{amsmath, amssymb, graphicx}
\usepackage{booktabs}

\title{Lanzarini Optimizer Series: Empirical Study of Curvature-Based Optimization from V1 to V17}
\author{Experimental AI Research Log}
\date{}

\begin{document}

\maketitle

\section{Abstract}

This document summarizes a full experimental exploration of custom optimization algorithms (V1–V17) designed to incorporate curvature, energy-aware updates, and K-FAC-like approximations into gradient-based learning. We analyze convergence, stability, and energy efficiency compared to AdamW.

\section{Introduction}

The goal of this study was to investigate whether curvature-aware optimizers can outperform standard first-order methods such as AdamW by introducing:

\begin{itemize}
    \item curvature proxies
    \item energy-aware updates
    \item Fisher/K-FAC approximations
    \item compression-based gradient transformations
\end{itemize}

\section{Methodology Overview}

All experiments used a consistent neural architecture:

\begin{itemize}
    \item Embedding layer (1000 $\rightarrow$ 64)
    \item Linear layers (64 $\rightarrow$ 128 $\rightarrow$ 1000)
    \item Cross entropy loss
    \item Sequence prediction task
\end{itemize}

Each optimizer was evaluated over multiple seeds with metrics:

\begin{itemize}
    \item Final loss
    \item Energy (sum of gradient magnitudes)
    \item Stability (variance of loss)
    \item Efficiency (loss / energy)
\end{itemize}

\section{Evolution of Optimizers}

\subsection{V1–V4: Early Curvature Proxies}

Initial versions attempted to incorporate:
\begin{itemize}
    \item curvature approximations via smoothing
    \item geometric updates
\end{itemize}

\textbf{Observation:}
No consistent improvement over AdamW.

\subsection{V5–V9: Compression-Based Methods}

Introduced:
\begin{itemize}
    \item gradient compression
    \item reduced update cost
\end{itemize}

\textbf{Result:}
Loss remained near baseline but no learning advantage observed.

\subsection{V10–V11: Hessian-Free Inspired Updates}

Introduced curvature proxies inspired by:
\begin{itemize}
    \item diagonal Hessian approximations
    \item trust-region style updates
\end{itemize}

\textbf{Result:}
Some unstable improvements, but inconsistent convergence.

\subsection{V12–V13: Instability Phase}

Large variance and unstable updates were observed:

\begin{itemize}
    \item loss spikes
    \item energy explosion
\end{itemize}

\textbf{Conclusion:}
Over-aggressive curvature modeling breaks optimization stability.

\subsection{V14–V15: Layer-wise Curvature Scaling}

Introduced layer-wise curvature scaling.

\textbf{Observation:}
\begin{itemize}
    \item stable training
    \item but no improvement in loss
    \item efficiency comparable or worse than AdamW
\end{itemize}

\subsection{V16: K-FAC Lite Approximation}

Attempted Kronecker-factorized curvature approximation.

\textbf{Issue:}
\begin{itemize}
    \item shape mismatches
    \item unstable matrix approximations
    \item loss degradation
\end{itemize}

Final result:

\begin{itemize}
    \item Adam loss $\approx 2.85$
    \item V16 loss $\approx 6.92$
    \item higher energy consumption
\end{itemize}

\subsection{V17: EMA Stabilized K-FAC Light}

Final version introduced:
\begin{itemize}
    \item exponential moving average of curvature
    \item diagonal preconditioning
    \item memory-safe approximation
\end{itemize}

\section{Final Experimental Results}

\subsection{AdamW Baseline}

\begin{itemize}
    \item Loss: 2.85
    \item Energy: 64.84
    \item Efficiency: 0.0439
\end{itemize}

\subsection{V17 Optimizer}

\begin{itemize}
    \item Loss: 6.92
    \item Energy: 445.34
    \item Efficiency: 0.0155
\end{itemize}

\section{Key Findings}

\subsection{1. Curvature Proxies Are Insufficient}

Simple diagonal or averaged curvature estimates fail to preserve meaningful second-order information.

\subsection{2. Normalization Destroys Gradient Signal}

Excessive normalization removes magnitude information essential for convergence.

\subsection{3. Lightweight K-FAC Approximations Are Not Effective}

Without eigenspectrum information, approximations behave as re-weighting operators rather than true preconditioners.

\section{Conclusion}

Across all tested versions (V1–V17), no optimizer consistently outperformed AdamW in terms of loss and efficiency.

However, the study reveals:

\begin{itemize}
    \item key failure modes of curvature-based optimizers
    \item instability of naive second-order approximations
    \item importance of preserving spectral information
\end{itemize}

\textbf{Final Insight:}

\begin{quote}
Lightweight curvature approximations without eigenspace structure do not provide meaningful optimization benefits over first-order methods.
\end{quote}

\end{document}

